Enter our title here

### 2017-08-08 manuscript.tex
started intro draft
Update manuscript.tex

It is no suprise that technology plays a vital role in practicing statistics and as the technological revolution continues to unfold, the use of statistical software has become increasingly emphasized in statistics education. By integrating the capabilities of technology in introductory statistics courses, students can explore statistical ideas by analyzing and interpreting real data sets (Chance2007), giving them an authentic view of how statistics is practiced outside of the classroom (Broaddus2013). The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education} (GAISE) College Report has also prompted the use of more technology in introductory courses.

>>>>

It is no suprise that technology plays a vital role in practicing statistics and as the technological revolution continues to 
unfold, the use of statistical software has become increasingly emphasized in statistics education. By integrating the 
capabilities of technology in introductory statistics courses, students can explore statistical ideas by analyzing and 
interpreting real data sets (Chance2007), giving them an authentic view of how statistics is practiced outside of the 
classroom (Broaddus2013). The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education} (GAISE) 
College Report has also prompted the use of more technology in introductory statistics courses, encouraging educators to use technology "as a way to explore conceptual ideas and enhance student learning" (AmericanStatisticalAssociation2016).
